Writing Trash Bin

### 2024-04-04 writingdumpster.qmd
added dumpster notes

# General thoughts/questions
- Does the flip (hypothesis test vs uncertainty visualisation) have mathematical implications in how the plots should be assessed? This implies a visible signal in an uncertainty plot should indicate some divergence from the null.
- This increased sensisitivity could be the result of another aspect of uncertainty that is ignored. Statstical tests are typically built upon a series of assumptions, and it is difficult to identify *which* assumption failure caused the data to fail the statistical tests. Lineup plots allow us to see *how* our data is different to the assumed distribution, and better understand *why* our data may have failled a test ^[Did Patricks paper compare statistical tests to lineup protocols in the event an earlier assumption of the tests, such as, independent observation? I think he did check some. I wonder if you can quantify the information difference you get from a rejected statistical test vs a rejected line plot]. 
- If information that can be used to calculate a statistic, but not the statistic itself, is shown, people will need to use a heuristic to extract that information which will decrease the precision with which that information is communicated. 
- put uncertainty in the context of other meta-data of variables

>>>>

## @Pu2020

## @Leland2005

# General thoughts/questions
- grammar of graphics describes what your visualisation *is* given the data you have. The reason the grammar of graphics is not equipt to handle uncertainty is the same reason the tidyverse is not equipt to handle it. It is generated and carries through between these independent steps.
  - unclear how uncertainty from the source would make it in.
  - Grammar of graphics describes what *is*. Uncertainty is what *might be*.
  - Every uncertainty visualisation is entirely definable within the grammar of graphics. The *difficulty* with implementing uncertainty does not come from a failing within the grammar of graphics but from the absent definition of uncertainty. Just like normal statistics, visual statistics defined by the grammar of graphics *must* be well defined, if they are not, they cannot be implemented in the grammar. 
- Does the flip (hypothesis test vs uncertainty visualisation) have mathematical implications in how the plots should be assessed? This implies a visible signal in an uncertainty plot should indicate some divergence from the null.
- This increased sensisitivity could be the result of another aspect of uncertainty that is ignored. Statstical tests are typically built upon a series of assumptions, and it is difficult to identify *which* assumption failure caused the data to fail the statistical tests. Lineup plots allow us to see *how* our data is different to the assumed distribution, and better understand *why* our data may have failled a test ^[Did Patricks paper compare statistical tests to lineup protocols in the event an earlier assumption of the tests, such as, independent observation? I think he did check some. I wonder if you can quantify the information difference you get from a rejected statistical test vs a rejected line plot]. 
- If information that can be used to calculate a statistic, but not the statistic itself, is shown, people will need to use a heuristic to extract that information which will decrease the precision with which that information is communicated. 
- put uncertainty in the context of other meta-data of variables
